Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)

### 2020-02-18 mstemc/index.tex
trivial modification

\section{Problem 1.32}
\label{sec:org919e435}

@@

Let \(T\) be the fundamental period of \(y_{2}(t)\), then based on the analysis
of \hyperref[Problem 1.32c]{Problem 1.32c} , we have \(x(t)\) is a speeded up version of \(y_{2}(t)\),
hense \(x(t)\) is periodic and has fundamental period \(\frac{T}{2}\).
\section{Problem 1.33}
\label{sec:org7dadf9d}

@@

Based on the fact that only integer is valid for the independent variable of
discrete-time signal, \(y_{2}[n]\) contains all the value of \(x[n]\) at the
even index whereas at the odd index \(y_{2}[n]= 0\).
\section{Problem 1.34}
\label{sec:org20cd069}

@@

Notice that \(x_{e}(t)x_{o}(t)\) is and odd signal, so \(\int_{-\infty}^{+\infty} x_{e}(t)x_{o}(t) dt = 0\)
\section{Problem 1.35}
\label{sec:orgcf4d953}

@@

When \(l = m/ \mathrm{gcd}(m,N)\), we have \(N_{0} = \frac{N}{ \mathrm{gcd}(m,N) }\).
\end{prf}
\end{document}

>>>>

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21-0.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

 \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
\hspace{0pt}\\

This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47d.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

 \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
\hspace{0pt}\\

This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}

\section{Problem 1.32}
\label{sec:orgfc1022f}

@@

Let \(T\) be the fundamental period of \(y_{2}(t)\), then based on the analysis
of \hyperref[Problem 1.32c]{Problem 1.32c} , we have \(x(t)\) is a speeded up version of \(y_{2}(t)\),
hense \(x(t)\) is periodic and has fundamental period \(\frac{T}{2}\).
\section{Problem 1.33}
\label{sec:orgc6b726e}

@@

Based on the fact that only integer is valid for the independent variable of
discrete-time signal, \(y_{2}[n]\) contains all the value of \(x[n]\) at the
even index whereas at the odd index \(y_{2}[n]= 0\).
\section{Problem 1.34}
\label{sec:org4fc36d2}

@@

Notice that \(x_{e}(t)x_{o}(t)\) is and odd signal, so \(\int_{-\infty}^{+\infty} x_{e}(t)x_{o}(t) dt = 0\)
\section{Problem 1.35}
\label{sec:orgd2ae89c}

@@

When \(l = m/ \mathrm{gcd}(m,N)\), we have \(N_{0} = \frac{N}{ \mathrm{gcd}(m,N) }\).
\end{prf}
\section{Problem 1.36}
\label{sec:org4a7f30f}

\begin{prob}[]{prob:1-36}
Let \(x(t)\) be the continuous-time complex exponential signal:
\begin{equation*}
x(t) = e^{i\omega_{0}t}
\end{equation*}
with fundamental frequency \(\omega_{0}\) and fundamental period \(T_{0} =
    2\pi /\omega_{0}\). Consider the discrete-time signal obtained by taking
equally spaced samples of \(x(t)\) --- that is,
\begin{equation*}
x[n] = x(nT) = e^{i\omega_{0}nT}
\end{equation*}

\begin{enumerate}
\item Show that \(x[n]\) is periodic if and only if \(T/T_{0}\) is a rational
number -- that is, if and only if some multiple of the sampling interval
exactly equals a multiple of the period of \(x(t)\).
\item Suppose that \(x[n]\) is periodic --- that is, that
\begin{equation}
\label{eq:1-36-1}
\frac{T}{T_{0}} = \frac{p}{q}
\end{equation}
where \(p\) and \(q\) are integers. What are the fundamental period and
fundamental frequency of \(x[n]\)? Express the fundamental frequency as a
fraction of \(\omega_{0}T\)
\item Again assuming that \(T/T_{0}\) satisfies eq (\ref{eq:1-36-1}), determine
precisely how many periods of \(x(t)\) are needed to obtain the samples
that form a single period of \(x[n]\).
\end{enumerate}
\label{prob:1-36}
\end{prob}

\textbf{Problem 1.36a}

\begin{prf}[]{}
Let \(N\) the fundamental period of \(x[n]\), then we have
\begin{equation*}
\omega_{0} N T = 2\pi m
\end{equation*}
So \(N = \frac{2\pi m}{\omega_{0}T}\), We also have \(T_{0}=
\frac{2\pi}{\omega_{0}}\), then
\begin{equation*}
N = m\frac{T_{0}}{T}
\end{equation*}
Then \(\frac{T_{0}}{T}\) must be a rational number so that \(m\frac{T_{0}}{T}\)
is an integer and \(N\) could be an integer i.e. \(x[n]\) is periodic.
\end{prf}

\textbf{Problem 1.36b}

Based on the analysis of Problem 1.36a, we have fundamental period of \(x[n]\)
\begin{equation*}
N = m\frac{T_{0}}{T} = m \frac{q}{p}
\end{equation*}
Where \(m\) is the minimum integer so that \(N\) is an integer. Based on the
conclusion of \hyperref[sec:orgd2ae89c]{Problem 1.35} , we can re-express \(N\) as
\begin{equation*}
N = \frac{q}{\mathrm{gcd}(p,q)}
\end{equation*}
Where \(m = \frac{p}{\mathrm{gcd}(p,q)}\).
The fundamental frequency is
\begin{equation*}
\frac{2\pi}{N} = \frac{2\pi \mathrm{gcd}(p,q)}{q} = \omega_{0}T_{0} \frac{\mathrm{gcd}(p,q)}{q} = \omega_{0}T\frac{\mathrm{gcd}(p,q)}{p}
\end{equation*}

\textbf{Problem 1.36c}

The fundamental period of \(x(t)\) is \(T_{0} = \frac{2\pi}{\omega_{0}}\) and
\(x[n]\) , \(N= \frac{q}{\mathrm{gcd}(p,q)}\). we have

\begin{equation*}
\frac{N}{T_{0}}= \frac{Np}{Tq} = \frac{q}{\mathrm{gcd}(p,q)T} \frac{p}{q} = \frac{p}{\mathrm{gcd}(p,q)T}
\end{equation*}
So, the discrete-time version of signal \(x(t)\) need at least
\(\frac{p}{\mathrm{gcd}(p,q)T}\) periods of \(x(t)\) to obtain one period of \(x[n]\).

Let's talk more about this problem. This problem preliminary discloses the concept
of sampling which is a main method of obtaining discrete-time signal from
continuous-time signal. Now let's put Nyquist's sampling theory aside and focus
on the sampling itself.

Suppose we have a continuous-time signal
\begin{equation*}
x(t) = \cos(4\pi t)
\end{equation*}
whose fundamental period is \(T_{0} = \frac{2\pi }{4\pi} = \frac{1}{2}\). Then
the sampling interval \(T\) must satisfies that \(T/T_{0}\) is a rational
number so that \(x[n]= x(nT)= \cos(4\pi nT )\) is a periodic signal.

Let \(T\), say, be \(\frac{1}{5}\), then
\begin{equation*}
\frac{T}{T_{0}} = \frac{2}{5}
\end{equation*}
The fundamental period of \(x[n]\) is \(N = \frac{q}{\mathrm{gcd}(p,q)} =
\frac{5}{\mathrm{gcd}(2,5)} = 5\).

We can visualize \(x(t)\) and \(x[n]\) as below.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-36-1.pdf}
\end{center}

From the above figure, we can see that the discrete-time signal \(x[n]\) has
fundamental period of \(5\) and its counterparts has fundamental period
\(\frac{1}{2}\). We need at least \(10\) period of \(x(t)\) to get one period of
\(x[n]\).

Now, if we take the Nyquist's sampling into consideration, we must sampling a
baseband signal with at least two times higher frequency of the signal to
recover the baseband signal without alias. i.e. we must sample \(x(t) =
\cos(4\pi t)\) with a signal of fundamental frequency \(8\pi\) to get signal
\(x[n] = \cos(8\pi n)\).
\section{Problem 1.37}
\label{sec:org5b0c999}

\begin{prob}[]{prob:1-37}
An important concept in many communications applications in the correlation
between two signals. In the problems at the end of Chapter 2, we will have
more to say about this topic and will provide some indication of how it is
used in practice. For now, we content ourselves with a brief introduction to
correlation functions and some of their properties.

Let \(x(t)\) and \(y(t)\) be two signals; then the correlation function is
defined as
\begin{equation*}
\phi_{xy}(t) = \int_{-\infty}^{+\infty} x(t+ \tau) y(\tau)d\tau
\end{equation*}

The function \(\phi_{xx}(t)\) is usually referred to as the autocorrelation
function of the signal \(x(t)\) , while \(\phi_{xy}(t)\) is often called a
cross-correlation function.

\begin{enumerate}
\item What is the relationship between \(\phi_{xy}(t)\) and \(\phi_{yx}(t)\) ?
\item Compute the odd part of \(\phi_{xx}(t)\).
\item Suppose that \(y(t)= x(t+ T)\). Express \(\phi_{xy}(t)\) and
\(\phi_{yy}(t)\) in terms of \(\phi_{xx}(t)\).
\end{enumerate}
\label{prob:1-37}
\end{prob}

\textbf{Problem 1.37a} \label{Problem 1.37a}

by the definition of correlation, we have
\begin{equation*}
\phi_{yx} = \int_{-\infty}^{+\infty} y(t + \tau)x(\tau) d \tau
\end{equation*}

we set \(t+ \tau = s\), then
\begin{eqnarray*}
\phi_{yx}(t) &=& \int_{-\infty}^{+\infty} y(t + \tau)x(\tau) d \tau \\
&=& \int_{-\infty}^{+\infty} x(s-t) y(s) ds \\
&=& \phi_{xy}(-t)
\end{eqnarray*}

Using the same procedure, we can also have \(\phi_{xy}(t) = \phi_{yx}(-t)\).

\textbf{Problem 1.37b}

we have
\begin{equation*}
\phi_{xx}(t) = \int_{-\infty}^{+\infty} x(t+\tau)x(\tau) d\tau
\end{equation*}
the odd part of \(\phi_{xx}(t)\) can be expressed as
\begin{equation*}
\phi_{oxx}(t) = \frac{\phi_{xx}(t) - \phi_{xx}(-t)}{2}
\end{equation*}

Based on \hyperref[Problem 1.37a]{Problem 1.37a}, we have \(\phi_{xx}(t) = \phi_{xx}(-t)\) , so
\(\phi_{oxx}(t) = 0\). which means that \(\phi_{oxx}(t)\) is an even signal.

\textbf{Problem 1.37c}

\begin{eqnarray*}
\phi_{xy}(t) &=& \int_{-\infty}^{+\infty} x(t+ \tau) y(\tau)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t+ \tau) x(\tau + T)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t + s -T) x(s) ds
\end{eqnarray*}
So we have \(\phi_{xy}(t) = \phi_{xx}(t-T)\).

\begin{eqnarray*}
\phi_{yy}(t) &=& \int_{-\infty}^{+\infty} y(t+ \tau) y(\tau)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t+ \tau + T) x(\tau + T)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t + s) x(s) ds
\end{eqnarray*}
So we have \(\phi_{yy}(t) = \phi_{xx}(t)\).
\section{Problem 1.38}
\label{sec:orgef628d7}

\begin{prob}[]{prob:1-38}
In this problem, we examine a few of the properties of the unit impulse
function.
\begin{enumerate}
\item show that
\begin{equation*}
\delta(2t) = \frac{1}{2} \delta(t)
\end{equation*}
Hint: Examine \(\delta_{\Delta}(t)\). (See Figure 1.34 in the textbook).
\item In Section 1.4, we defined the continuous-time unit impulse as the limit
of the signal \(\delta_{\Delta}(t)\). More precisely, we defined several
of the properties of \(\delta(t)\) by examining the corresponding
properties of \(\delta_{\Delta}(t)\). For example, since the signal
\begin{equation*}
u_{\Delta}(t) = \int_{-\infty}^{t}\delta_{\Delta}(\tau)d\tau
\end{equation*}
converges to the unit step:
\begin{equation*}
u(t) = \lim_{\Delta\to 0} u_{\Delta}(t),
\end{equation*}
we could interpret \(\delta(t)\) through the equation
\begin{equation}
\label{eq:problem1-38-1}
u(t) = \int_{-\infty}^{t} \delta(\tau)d\tau
\end{equation}
or by viewing \(\delta(t)\) as the formal derivative of \(u(t)\).

This type of discussion is important, as we are in effect trying to
define \(\delta(t)\) through its properties rather than by specifying its
value for each \(t\), which is not possible. In Chapter 2, we provide a
very simple characterization of the behavior of the unit impulse that is
extremely useful in the study of linear time-invariant systems. For the
present, however, we concentrate on demonstrating that the important
concept in using the unit impulse is to understand how it behave. To do
this, consider the six signals depicted in Figure shown below. Show that
each "behaves like an impulse" as \(\Delta\to 0\) in that, if we let
\begin{equation*}
u_{\Delta}^{i}(t) = \int_{-\infty}^{t} r_{\Delta}^{i}(\tau)d\tau,
\end{equation*}
then
\begin{equation*}
\lim_{\Delta\to 0} u_{\Delta}^{i}(t) = u(t)
\end{equation*}
In each case, sketch and label carefully the signal
\(u_{\Delta}^{i}(t)\). Note that
\begin{equation*}
r_{\Delta}^{2}(0) = r_{\Delta}^{4}(0) = 0 \ \forall \Delta
\end{equation*}
Therefore, it is not enough to define or to think of \(\delta(t)\) as
being zero for \(t\neq 0\) and infinite for \(t=0\). Rather, it is
properties such as equation (\ref{eq:problem1-38-1}) that define the
impulse. In Section 2.5 we will define a whole class of signals known as
singularity function, which are related to the unit impulse and which are
also defined in terms of their properties rather than their values.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38-2.pdf}
\end{center}
\end{enumerate}
\label{prob:1-38}
\end{prob}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38-0.pdf}
\label{figProb1-38-0}
\end{center}

\textbf{Problem 1.38a}

Base on fig \ref{figProb1-38-0} , \(\delta(2t)\) can be visualized as follows

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38-1.pdf}
\end{center}

Based on the fact \(\delta(t)\) has unit area, so \(\delta(2t)\) will have
\(\frac{1}{2}\) . So \(\delta(2t) = \frac{1}{2}\delta(t)\).

\textbf{Problem 1.38b}

Because
\begin{equation*}
u_{\Delta}(t) = \int_{-\infty}^{t}\delta_{\Delta}(\tau)d\tau
\end{equation*}
We can get \(u_{\Delta}^{1}(t)\) easily.

\(r_{\Delta}^{1}(t)\) can be represented as
\begin{equation*}
r_{\Delta}^{1}(t) =
\begin{cases}
\frac{1}{\Delta}, & -\frac{\Delta}{2} \leq t \leq \frac{\Delta}{2} \\
               0, & \mathrm{Otherwise}
\end{cases}
\end{equation*}

Then during the integration, \(u_{\Delta}^{1}(t)\) can be represented as
\begin{equation*}
u_{\Delta}^{1}(t) =
\begin{cases}
0, &  t < -\frac{\Delta}{2} \\
\frac{t}{\Delta}, & -\frac{\Delta}{2} \leq t \leq \frac{\Delta}{2} \\
1, & t > \frac{\Delta}{2}
\end{cases}

\end{equation*}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38b.pdf}
\end{center}

we can express the \(r_{\Delta}^{2}(t)\) as :
\begin{equation*}
r_{\Delta}^{2}(t) =
\begin{cases}
\frac{1}{\Delta} , & \Delta \leq t \leq 2\Delta \\
0, & \mathrm{Otherwise}
\end{cases}
\end{equation*}

So the \(u_{\Delta}^{2}(t)\) can be expressed as:
\begin{equation*}
u_{\Delta}^{2}(t) =
\begin{cases}
0, & t < \Delta \\
\frac{t-\Delta}{\Delta} & \Delta \leq t \leq 2\Delta \\
1, & t> 2\Delta
\end{cases}
\end{equation*}
\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38c.pdf}
\end{center}

We express \(r_{\Delta}^{3}(t)\) as:
\begin{equation*}
r_{\Delta}^{3}(t) =
\begin{cases}
\frac{1}{\Delta^{2}} ( t +  \Delta) , & - \Delta < t \leq 0 \\
\frac{1}{\Delta^{2}} ( -t + \Delta) , & 0 < t \leq \Delta \\
0, & \mathrm{otherwise}
\end{cases}
\end{equation*}
and \(u_{\Delta}^{3}(t)\):

\begin{equation*}
u_{\Delta}^{3}(t) =
\begin{cases}
\frac{1}{\Delta^{2}}( \frac{t^{2}}{2} + \Delta t + \frac{\Delta^{2}}{2}) ,& -\Delta < t \leq  0 \\
\frac{1}{2} + \frac{1}{\Delta^{2}} ( - \frac{t^{2}}{2} + \Delta t ) , & 0 < t < \Delta \\
1, & t > \Delta
\end{cases}
\end{equation*}

So we can visualize them as follows:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38d.pdf}
\end{center}

We can represent \(r_{\Delta}^{4}(t)\) as :
\begin{equation*}
r_{\Delta}^{4}(t) =
\begin{cases}
- \frac{1}{\Delta^{2}} t , &  -\Delta < t \leq 0 \\
\frac{1}{\Delta^{2}} t , &   0 < t \leq \Delta  \\
0, & \mathrm{Otherwise}
\end{cases}
\end{equation*}

and \(u_{\Delta}^{4}(t)\)

\begin{equation*}
u_{\Delta}^{4}(t) =
\begin{cases}
0, &  t < -\Delta \\
- \frac{t^{2}}{2\Delta^{2}} + \frac{1}{2}, & - \Delta < t \leq 0\\
 \frac{t^{2}}{2\Delta^{2}} + \frac{1}{2}, & - \Delta < t \leq 0\\
1, & t > \Delta
\end{cases}
\end{equation*}
and we visualize them as:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38e.pdf}
\end{center}

We can express \(r_{\Delta}^{5}(t)\) as :
\begin{equation*}
r_{\Delta}^{5}(t) =
\begin{cases}
- \frac{1}{\Delta} , & -\Delta < t \leq 0 \\
\frac{2}{\Delta} , & 0 < t \leq \Delta \\
0, & \mathrm{Otherwise}
\end{cases}
\end{equation*}

and \(u_{\Delta}^{5}(t)\) as:

\begin{equation*}
u_{\Delta}^{5}(t) =
\begin{cases}
- \frac{t}{\Delta} -1, & -\Delta < t < 0 \\
-1 + \frac{2t}{\Delta} , & 0 < t \leq \Delta \\
1,& t > \Delta
\end{cases}
\end{equation*}
So we can visualize them as below:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38f.pdf}
\end{center}

We can express \(r_{\Delta}^{6}(t)\) as :
\begin{equation*}
r_{\Delta}^{6}(t) = \frac{1}{2\Delta} e^{-|t|/\Delta}
\end{equation*}

and \(u_{\Delta}^{6}(t)\) as :
\begin{equation*}
u_{\Delta}^{6}(t) =
\begin{cases}
\frac{1}{2} e^{\frac{t}{\Delta}} , & t< 0 \\
1 - \frac{1}{2}e^{ \frac{-t}{\Delta}} , & t> 0 \\
\end{cases}
\end{equation*}
So we can visualize them as below:
\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38g.pdf}
\end{center}
\section{Problem 1.39}
\label{sec:org95fdb02}

\begin{prob}[]{prob:1-39}
The role played by \(u(t)\) and \(\sigma(t)\) and other singularity
functions in the study of linear time-invariant systems is that of an
idealization of a physical phenomenon, and, as we will see, the use of these
idealizations allow us to obtain an exceedingly important and very simple
representation of such systems. In using singularity functions, we need,
however, to be careful. In particular, we must remember that they are
idealizations, and thus, whenever we perform a calculation using them, we
are implicitly assuming that this calculation represents an accurate
description of the behavior of the signals that they are intended to
idealize. To illustrate, consider the equation
\begin{equation}
\label{eq:prob1-39-0}
x(t)\sigma(t) = x(0)\sigma(t)
\end{equation}
This equation is based on the observation that
\begin{equation}
\label{eq:prob1-39-1}
x(t)\sigma_{\Delta}(t) \approx x(0)\sigma_{\Delta}(t)
\end{equation}
Taking the limit of this relationship then yields the idealized one given by
equation (\ref{eq:prob1-39-0}). However, a more careful examination of our
derivation of equation (\ref{eq:prob1-39-1}) shows that that equation really
makes senses only if \(x(t)\) is continuous at \(t=0\). If it is not, then
we will not have \(x(t)\approx x(0)\)  for \(t\) small.

To make this point clearer, consider the unit step signal \(u(t)\). Recall
from the following equation:
\begin{equation*}
u(t) =
\begin{cases}
  0, & t< 0\\
  1, & t> 0
\end{cases}
\end{equation*}
that

\begin{enumerate}
\item \(u(t)= 0\) for \(t<0\)
\item \(u(t) = 1\) for \(t> 0\),
\end{enumerate}

but that its value at \(t=0\) is not defined. The fact that \(u(0)\) is not
defined is not particularly bothersome, as long as the calculations we
perform using \(u(t)\) do not rely on a specific choice for \(u(0)\). For
example, if \(f(t)\) is a signal that is continuous at \(t=0\), then the
value of
\begin{equation*}
\int_{-\infty}^{+\infty} f(\sigma) u(\sigma) d \sigma
\end{equation*}
does not depend upon a choice for \(u(0)\). On the other hand, the fact that
\(u(0)\) is undefined is significant in that it means that certain
calculations involving singularity functions are undefined. Consider trying
to define a value for the product \(u(t)\delta(t)\).

To see that this cannot be defined, show that
\begin{equation*}
\lim_{\Delta\to 0} [u_{\Delta}(t)\delta(t)] = 0,
\end{equation*}
but
\begin{equation*}
\lim_{\Delta\to 0} [u_{\Delta}(t)\delta_{\Delta}(t)] = \frac{1}{2} \delta(t)
\end{equation*}

In general, we can define the product of two signals without any difficulty,
as long as the signals do not contain  singularities  ( discontinuities,
impulse, or the other singularities introduced in Section 2.5) whose
locations coincide. When the locations do coincide, the product is
undefined. As an example, show that the signal
\begin{equation*}
g(t) = \int_{-\infty}^{+\infty} u( \tau )\delta(t-\tau)d\tau
\end{equation*}
is identical to \(u(t)\); that is, it is \(0\) for \(t < 0\), it equals
\(1\) for \(t> 0\), and it is undefined for \(t=0\)
\label{prob:1-39}
\end{prob}

\begin{equation*}
\lim_{\Delta\to 0} [u_{\Delta}(t)\delta(t)] = \lim_{\Delta\to 0} [u_{\Delta}(t)\delta(0)] = 0
\end{equation*}

And
\begin{eqnarray*}
\lim_{\Delta\to 0} [u_{\Delta}(t)\delta_{\Delta}(t)] &=& \lim_{\Delta\to 0 } \frac{1}{2} \frac{d u_{\Delta}^{2}(t)}{dt} \\
&=& \frac{1}{2} \delta(t)
\end{eqnarray*}
Notice that when \(\Delta\to 0\) the item  \(\frac{u_{\Delta}^{2}(t)}{dt}\)
also approach to \(\delta(t)\).

for equation:
\begin{equation*}
g(t) = \int_{-\infty}^{+\infty} u( \tau )\delta(t-\tau)d\tau
\end{equation*}
we have
\begin{equation*}
g(t) =
\begin{cases}
0, & t< 0 \\
1, & t> 0 \\
\mathrm{undefined}, & t = 0
\end{cases}

\end{equation*}
So \(g(t)\) has the same property as \(u(t)\)
\section{Problem 1.40}
\label{sec:org71282a6}

\begin{prob}[]{prob:1-40}
\begin{enumerate}
\item Show that if a system is either additive or homogeneous, it has the
property that if the input is identically zero, then the output is also
identically zero.
\item Determine a system (either in continuous or discrete time) that is
neither additive nor homogeneous but which has a zero output if the input
is identically zero.
\item From part (a) can you include that if the input to a linear system is
zero  between times \(t_{1}\) and \(t_{2}\) in continuous time or between
times \(n_{1}\) and \(n_{2}\) in descrete time, then its output must also
be zero between these same times? Explain your answer.
\end{enumerate}
\label{prob:1-40}
\end{prob}

\textbf{Problem 1.40a}

\begin{prf}[]{}
Let \(x_{1}(t)\) and \(x_{2}(t)\) be two input signals of system
\(\mathcal{S}\), and \(y_{1}(t)\) and \(y_{2}(t)\) two output respectively. The
system is represented as \(y(t) = f(x(t))\). Then
\begin{eqnarray*}
y_{1}(t)&=& f(x_{1}(t)) \\
y_{2}(t)&=& f(x_{2}(t))
\end{eqnarray*}
Let \(x_{3}(t)= x_{1}(t) + x_{2}(t)\), then by the definition of additive
property
\begin{equation*}
y_{3}(t) = f(x_{3}(t)) = f(x_{1}(t) + x_{2}(t)) = y_{1}(t) + y_{2}(t)
\end{equation*}
If \(x_{1}(t)= x_{2}(t) = 0\) , then \(x_{3}(t) = 0\) and we have
\begin{equation*}
f(0) = 2f(0)
\end{equation*}
So, \(f(0) = 0\). i.e. If a system is additive and the input is identically
zero, then the output is also identically zero.

Next we show that if a system is homogeneous, the property also holds.

Let \(x_{1}(t)\) be input signals of system \(\mathcal{S}\), and \(x_{2}(t)= \alpha
x_{1}(t)\) another input. we have
\(y_{1}(t) = f(x_{1}(t))\) and \(y_{2}(t) = f(x_{2}(t)) = \alpha f(x_{1}(t))\).
If \(x_{1}(t)  = 0\), then \(x_{2}(t) = 0\) so \(y_{2}(t) = f(0) = \alpha
f(0)\). Then we have \(f(0) = 0 = y_{2}(t)\). i.e. if a system is homogeneous
and the input is identically zero, then the output is also identically zero.
\end{prf}

\textbf{Problem 1.40b}

It is easy to construct such a system, for a continuous-time version, we have
\(y(t) = x^{2}(t)\) and it discrete-time counterparts \(y[n] = x^{2}[n]\)

We cannot reach that conclusion. Because for a system has memory, a certain
zero period \(t_{1}\) to \(t_{2}\) does not result the same zero period in the
output. Let's take \(y[n] = x[n-n_{0}]\) where \(n_{0}\neq 0\), the output will
have a delay ( \(n_{0}\) is positive) and an advance ( \(n_{0}\) is negative).
\section{Problem 1.41}
\label{sec:orgb5785da}

\begin{prob}[]{prob:1-41}
Consider a system \(\mathcal{S}\) with input \(x[n]\) and output \(y[n]\)
related by
\begin{equation*}
y[n] = x[n]\{ g[n] + g[n-1] \}
\end{equation*}

\begin{enumerate}
\item If \(g[n] = 1\) for all \(n\), show that \(S\) is time invariant.
\item If \(g[n] = n\) , show that \(\mathcal{S}\) is not time invariant.
\item If \(g[n] = 1 + (-1)^{n}\), show that \(\mathcal{S}\) is time invariant.
\end{enumerate}
\label{prob:1-41}
\end{prob}

\textbf{Problem 1.41a}

If \(g[n] = 1 \forall \ n\) , then we have
\begin{equation*}
y[n] = 2x[n]
\end{equation*}

Next, we proof that this system is time invariant. Let \(x_{1}[n]\) and
\(y_{1}[n]\) are the input and output respectively i.e.
\begin{equation*}
y_{1}[n] = 2x_{1}[n]
\end{equation*}
Let \(x_{2}[n] = x_{1}[n-n_{0}]\) then we have
\begin{equation*}
y_{2}[n] = 2x_{2}[n] = 2x_{1}[n-n_{0}] = 2y_{1}[n-n_{0}]
\end{equation*}
So we have that one time shift in the input signal will result in an identical
time shift in the output. The system is time invariant.

if \(g[n] = n\), we have
\begin{equation*}
y[n] = (2n-1) x[n]
\end{equation*}

Let \(x_{1}[n]\) and \(y_{1}[n]\) the input and output respectively, i.e.
\begin{equation*}
y_{1}[n] = (2n-1)x_{1}[n]
\end{equation*}

Let \(x_{2}[n] = x_{1}[n-n_{0}]\), then we have
\begin{equation*}
y_{2}[n] = (2n-1)x_{2}[n] = (2n-1)x_{1}[n-n_{0}]
\end{equation*}

We also have:
\begin{equation*}
y_{1}[n-n_{0}] = ( 2(n-n_{0}) ) x_{1}[n-n_{0}]
\end{equation*}
Obviously, \(y_{2}[n]\neq y_{1}[n-n_{0}]\). The system is time invariant.

If \(g[n] = 1 + (-1)^{n}\), then
\begin{equation*}
g[n] + g[n-1] = 1 + (-1)^{n} + 1 + (-1)^{n-1} = 2
\end{equation*}

Which means that the system is identical as the system in part (a) and hence the
system is time invariant.
\section{Problem 1.42}
\label{sec:org8f471d7}

\begin{prob}[]{prob:1-42}
\begin{enumerate}
\item Is the following statement true or false?

The series interconnection of two linear time-invariant system is itself
a linear, time-invariant system.

Justify your answer.

\item Is the following statement true or false?

The series interconnection of two nonlinear systems is itself nonlinear.

Justify your answer.

\item Consider three systems with the following input-output relationships:

System 1:

\begin{equation*}
 y[n] =
 \begin{cases}
 x[n/2], & n\ \mathrm{even} \\
 0, & n\ \mathrm{odd}
 \end{cases}
\end{equation*}

System 2:

\begin{equation*}
y[n]  = x[n] + \frac{1}{2}x[n-1] + \frac{1}{4}x[n-2]
\end{equation*}

System 3:
\begin{equation*}
y[n] = x[2n]
\end{equation*}

Suppose that these systems are connected in series as depicted in Figure
below. Find the input-output relationship for the overall interconnected
system. Is this system linear? Is it time invariant?
\end{enumerate}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-42.pdf}
\end{center}
\label{prob:1-42}
\end{prob}

Let \(\mathcal{S}_{1}\) and \(\mathcal{S}_{2}\) two connected LTI system. Let
\(x_{11}(t)\) and \(x_{12}(t)\) arbitrary signals, \(a_{1}\) and \(b_{1}\)
arbitrary consstants.

Then:
\begin{eqnarray*}
x_{11}(t)&\xrightarrow{\mathcal{S}_{1}} & y_{11}(t)  \\
x_{12}(t)&\xrightarrow{\mathcal{S}_{1}} & y_{12}(t)  \\
\end{eqnarray*}
Let \(x_{13}(t) = a_{1} x_{11}(t) + b_{1}x_{12}(t)\), then
\begin{equation*}
x_{13}(t)  = a_{1} x_{11}(t) + b_{1}x_{12}(t) \xrightarrow{\mathcal{S}_{1}}  y_{13}(t) = a_{1}y_{11}(t) + b_{1} y_{12}(t)
\end{equation*}
